Combined Task and Motion Planner through an Interface Layer

### 2015-05-14 documentation/ps4.tex
Changes to final paper

\subsection{Square Grid}
We ran the square grid scenario on a simulated Baxter robot.
The planner took approximately an hour to find a feasible plan. 
In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
A video of the successful test trial in simulation can be found at [TODO: link here].  
We did not run this test on the real Baxter robot.

@@

Task & \shortstack{Number of \\Blocks} & \shortstack{Blocks to Move} & \shortstack{Number of \\TP Calls} & \shortstack{Number of \\MP Calls} & Runtime \\ \hline
Square Grid & 9 & 1 & ? & ? & ?\\
\hline
Sorting & 9 & 9 & ? & ? & ?\\
\hline

@@

[3] I. A. Sucan and Sachin Chitta, ``MoveIt!''. [Online] Available: http://moveit.ros.org

>>>>

\subsection{Square Grid}
We ran the square grid scenario on a simulated Baxter robot.
The planner took approximately an hour to find a feasible plan. 
In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
A video of the successful test trial in simulation can be found at \url{http://youtu.be/Jb9EOZ8B2lU}.  
We did not run this test on the real Baxter robot.

@@

Task & Trial & \shortstack{Number of \\Blocks} &\shortstack{Blocks to Move} & \shortstack{Number of \\TP Calls} & \shortstack{Number of \\MP Calls} & Runtime (min) \\ \hline
Square Grid & 1 & 9 & 1 & 3 & 721 & 21.45\\
\hline
 & 2 &  &  & 3 & 1376 & 86.98\\
\hline
 & 3 &  &  & 3 & 1198 & 80.11\\
\hline
 & \textbf{Avg} &  &  & \textbf{3} & \textbf{1098.33} & \textbf{62.85}\\

\hline
Sorting & 1 & 9 & 9 & 8 & 353 & 22.33\\
\hline
 & 2 &  &  & 6 & 304 & 15.97\\
\hline
 & 3 &  &  & 6 & 379 & 20.76\\
 \hline
 & \textbf{Avg} &  &  & \textbf{6.67} & \textbf{345.33} & \textbf{19.69}\\

@@

[3] I. A. Sucan and Sachin Chitta, ``MoveIt!''. [Online] Available: \url{http://moveit.ros.org}
